Algorithm Selection for Graph Algorithms

### 2015-12-18 portfolio/as-graphs.Rnw
random changes

@@

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
write.csv(wide, file = "no-presolved-presolver-allinstances.csv", row.names = FALSE)
p.full = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    guides(col = guide_legend(ncol = 2, keyheight = .8)) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.5), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))

>>>>

print(xtable(table(singleBest(ldf2)$algorithm)))

@@

print(xtable(table(singleBest(ldf)$algorithm)))

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
write.csv(wide, file = "no-presolved-presolver-allinstances.csv", row.names = FALSE)

#rs = asscenario$feature.runstatus[c("instance_id", "lad_features")]
#fc = asscenario$feature.costs[c("instance_id", "lad_features")]
#sc = merge(rs, fc, by = "instance_id")
#sc$time = sc$lad_features.y
#sc$time[sc$lad_features.x != "presolved"] = 10^8
#foo = rbind.fill(lapply(unique(wide$instance_id), function(id) { data.frame(instance_id = id, solver = "virtual.best.lad", time = min(sc$time[sc$instance_id == id], wide$time[wide$solver == "virtual.best"&wide$instance_id == id]), type = "pf") }))
#newwide = rbind(wide, foo)
